---
title: "Survey Text Analysis"
author: "Chris Selig"
date: "10/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = F,
    warning = F,
    message = F
    )
```

```{r load libraries}
# Workhorse: data manipulation, plotting
library(tidyverse)
library(janitor)

# Read in data
library(readxl)

# Text specific packages
library(tidytext)
library(stopwords)

# Visualization packages
library(ggthemes)
```


```{r load data}
raw_data <- read_excel("../00_data/survey_text_responses.xlsx",sheet = "Survey_responses")
keyword <- read_excel("../00_data/keywords.xlsx")
```

```{r source scripts}
source("../01_scripts/01_data_processing.R")
```

```{r set theme for plots}
# Set theme
theme_set(theme_tufte())
```


```{r unigrams data processing}
unigram_tidy_data <- raw_data %>% 
    clean_column_names_function() %>% 
    tokenize_data_function() %>% 
    remove_stop_words_function()
```

## Purpose

The purpose of this analysis is to analyze the four open ended questions in a survey for customer satisfaction for VHT's products.

The four questions are:

1. If you could change anything about the services VHT Studios offers, what would it be?


2. What can we do better?

3. What other capabilities would you be interested in VHT offering?

4. Additional Comments and/or Suggestions for improvements or changes



## Visualize Most Common Single Words


The below image shows the single most frequent words that appear on each of the four open ended questions.
```{r unigram visual}
unigram_tidy_data %>% 
    count(question, word) %>%
    group_by(question) %>%
    arrange(desc(n)) %>%
    top_n(10) %>% 
    ungroup() %>% 
    mutate(
        question = as.factor(question),
        word = reorder_within(word, n, question)
    ) %>% 
    mutate(
        question = str_replace(question, "open_",""),
        question = str_replace_all(question, "_"," "),
        question = str_to_title(question)
    ) %>% 
    ggplot(aes(word,n)) +
    geom_bar(stat = 'identity',aes(fill = n), fill = '#A2AAB0') +
    coord_flip() +
    geom_text(aes(label = n), size = 3, hjust = 1.4, color = 'black') +
    facet_wrap(~question,scales = "free") +
    scale_x_reordered() +
    labs(
        x = '',
        y = '',
        title = "Top 10 Single Words for Each Open Question"
    ) +
    theme(
        plot.title = element_text(size = 14, family = "memphis",color = '#4C586F', face = 'bold'),
        plot.subtitle = element_text(hjust = 0.01, size = 11,family = "ArnoProLightDisplay"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none"
    )
```


